\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2013-08-07 Compiled/chapter4/sections/Collaboration-Use-Cases.tex
Added copyright information for reused figures

\begin{figure}[tbp]
   \begin{subfigure}[]{0.4\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures-pdf/snapshot_nond}}
   \caption{Unbiased Gnutella}%
   \end{subfigure}
\hfill
   \begin{subfigure}[]{0.45\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures-pdf/snapshot_nd}}
   \caption{Gnutella with Oracle}%
   \end{subfigure}   \caption{Visualization of Gnutella overlay topology}
   \label{fig:oracle:gnutella_topology}
\end{figure}

@@

\begin{figure}[tbp]
  \center\includegraphics[width=0.8\linewidth]{figures-pdf/trafficShift-concept}
  \caption{By choosing a CDI server for a client with the help of CaTE, traffic
  engineering goals and accurate end-user server assignment become possible.}
  \label{fig:flowSelection}
  \vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
    \center \includegraphics[width=3.2in]{figures-pdf/CaTE_Schematic}
  \vspace{-0.1in}
    \caption{CaTE System architecture and flow of messages.}
    \label{fig:CaTE-architecture}
    \vspace{-0.2in}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=0.90\linewidth]{figures-pdf/trafficShift-illustration}
\caption{Content-aware Traffic Engineering Process}
\label{fig:Content-aware-illustration2}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/providersVsVolume}
\caption{CDF of traffic volume of CDIs in ISP1.}
\label{fig:CDF-Traffic-CPs}
\vspace{-1.5em}
\end{figure}

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/Volume_timeseries}
\caption{Normalized traffic for top CDIs by volume in ISP1.}
\label{fig:CPs-Total-Traffic}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center
\includegraphics[width=1\linewidth]{figures-pdf/SubnetChoice_r-2}
\caption{Evolution over time of number of subnets for selected CDIs in the top 10 CDIs.}
\label{fig:TemporalEffect}
\vspace{-1.5em}
\end{figure}

>>>>

\begin{figure}[tbp]
   \begin{subfigure}[]{0.4\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures-pdf/snapshot_nond}}
   \caption{Unbiased Gnutella}%
   \end{subfigure}
\hfill
   \begin{subfigure}[]{0.45\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures-pdf/snapshot_nd}}
   \caption{Gnutella with Oracle}%
   \end{subfigure}   \caption{Visualization of Gnutella
     overlay topology. Reprinted from \cite{afs-cispp2pcip-ccr07}. Included here by permission.}
   \label{fig:oracle:gnutella_topology}
\end{figure}

@@

\begin{figure}[tbp]
  \center\includegraphics[width=0.8\linewidth]{figures-pdf/trafficShift-concept}
  \caption{By choosing a CDI server for a client with the help of CaTE, traffic
  engineering goals and accurate end-user server assignment become
  possible. Reprinted from \cite{Cate-CCR}. Included here by permission.}
  \label{fig:flowSelection}
  \vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
    \center \includegraphics[width=3.2in]{figures-pdf/CaTE_Schematic}
  \vspace{-0.1in}
    \caption{CaTE System architecture and flow of messages. Reprinted from \cite{Cate-CCR}. Included here by permission.}
    \label{fig:CaTE-architecture}
    \vspace{-0.2in}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=0.90\linewidth]{figures-pdf/trafficShift-illustration}
\caption{Content-aware Traffic Engineering Process. Reprinted from \cite{Cate-CCR}. Included here by permission.}
\label{fig:Content-aware-illustration2}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/providersVsVolume}
\caption{CDF of traffic volume of CDIs in ISP1. Reprinted from \cite{Cate-CCR}. Included here by permission.}
\label{fig:CDF-Traffic-CPs}
\vspace{-1.5em}
\end{figure}

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/Volume_timeseries}
\caption{Normalized traffic for top CDIs by volume in ISP1. Reprinted from \cite{Cate-CCR}. Included here by permission.}
\label{fig:CPs-Total-Traffic}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center
\includegraphics[width=1\linewidth]{figures-pdf/SubnetChoice_r-2}
\caption{Evolution over time of number of subnets for selected CDIs in
  the top 10 CDIs. Reprinted from \cite{Cate-CCR}. Included here by permission.}
\label{fig:TemporalEffect}
\vspace{-1.5em}
\end{figure}

### 2013-08-07 Compiled/chapter4/sections/Content-Delivery-Overview.tex
Fix compilation of chapter4 with new pdf files for figures
Added copyright information for reused figures

\begin{figure} \begin{center}
\includegraphics[width=0.7\linewidth]{figures/flows-example.eps} 
\end{center}
\caption{Example of CDI deployment and traffic flows (Web traffic demands).}
\label{fig:aka:cdn} \end{figure}

\begin{figure} 
\begin{center}
\includegraphics[width=0.6\linewidth]{figures/page.eps}
\vspace*{-.7cm}
\end{center}
\caption{Example Web page with some CDI content.}
\label{fig:aka:cdn_page}
\end{figure}

>>>>

\begin{figure} \begin{center}
\includegraphics[width=0.7\linewidth]{figures-pdf/flows-example} 
\end{center}
\caption{Example of CDI deployment and traffic flows (Web traffic
  demands). Reprinted from \cite{inferring-web-demand}, \copyright ACM, 2004. Included here by permission.}
\label{fig:aka:cdn} \end{figure}

\begin{figure} 
\begin{center}
\includegraphics[width=0.6\linewidth]{figures-pdf/page}
\vspace*{-.7cm}
\end{center}
\caption{Example Web page with some CDI content. Reprinted from \cite{inferring-web-demand}, \copyright ACM, 2004. Included here by permission.}
\label{fig:aka:cdn_page}
\end{figure}

### 2013-08-07 Compiled/chapter4/sections/Traffic-Trends-Server-Diversity.tex
Added copyright information for reused figures

\begin{figure}[htbp]
  \centering
  \includegraphics[height=0.7\linewidth]{figures-pdf/dns-diversity}
  \caption{DNS replies for two different sites hosted on a CDI, in two-hour bins}%
  \label{fig:dns_diversity}
\end{figure}

@@

  \caption{CCDF of mean \# of IPs (top) and subnets (bottom) per DNS reply for the ISPs DNS resolver.}
  \label{fig:CDF-AVG-REPLY-IPs}
\end{figure}

@@

\begin{figure}[htbp]
  \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/14day-returnedIPCDF-bytes}
   \includegraphics[height=0.7\linewidth]{figures-pdf/14day-returnedIPCDF-hits}
  \caption{CDF of \# of IPs for the ISP DNS resolver normalized by traffic
    volume  (top) and requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.)}
  \label{fig:CDF-IPPAF-IPs}
\end{figure}

\begin{figure}[htbp]
  \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/SubnetsByBytes}
   \includegraphics[height=0.7\linewidth]{figures-pdf/SubnetsByHits}
  \caption{CDF of \# of subnets for ISP DNS resolver normalized by traffic
    volume  (top) and by requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.)}
  \label{fig:CDF-IPPAF-Subnets}
\end{figure}

@@

We find that more than $50$\perc of the volume or requests can be served by
more than one IP address. Similarly, there is choice between at least two
subnets over $40$\perc of the time across both metrics, see Figure~\ref
{fig:CDF-IPPAF-Subnets}. This indicates that there is significant potential for
the ISP to bias the location preference of the CDI.
\clearpage
\begin{figure}[htbp]
  \center\includegraphics[height=0.7\linewidth]{figures-pdf/maxTTLCDF}
  \caption{CDF of DNS TTL value by traffic volume and by number of requests.}
  \label{fig:CDF-IPPAF-TTL}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[height=0.7\linewidth]{figures-pdf/dns-diversity}
  \caption{DNS replies for two different sites hosted on a CDI, in two-hour bins.  Reprinted from \cite{PADIS2010}, \copyright ACM, 2010. Included here by permission.}%
  \label{fig:dns_diversity}
\end{figure}

@@

  \caption{CCDF of mean \# of IPs (top) and subnets (bottom) per DNS reply for the ISPs DNS resolver. Reprinted from \cite{PADIS2010}, \copyright ACM, 2010. Included here by permission.}
  \label{fig:CDF-AVG-REPLY-IPs}
\end{figure}

@@

\begin{figure}[htbp]
  \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/14day-returnedIPCDF-bytes}
   \includegraphics[height=0.7\linewidth]{figures-pdf/14day-returnedIPCDF-hits}
  \caption{CDF of \# of IPs for the ISP DNS resolver normalized by traffic
    volume  (top) and requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.) Reprinted from \cite{PADIS2010}, \copyright ACM, 2010. Included here by permission.}
  \label{fig:CDF-IPPAF-IPs}
\end{figure}

\begin{figure}[htbp]
  \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/SubnetsByBytes}
   \includegraphics[height=0.7\linewidth]{figures-pdf/SubnetsByHits}
  \caption{CDF of \# of subnets for ISP DNS resolver normalized by traffic
    volume  (top) and by requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.) Reprinted from \cite{PADIS2010}, \copyright ACM, 2010. Included here by permission.}
  \label{fig:CDF-IPPAF-Subnets}
\end{figure}

@@

We find that more than $50$\perc of the volume or requests can be served by
more than one IP address. Similarly, there is choice between at least two
subnets over $40$\perc of the time across both metrics, see Figure~\ref
{fig:CDF-IPPAF-Subnets}. This indicates that there is significant potential for
the ISP to bias the location preference of the CDI.
\clearpage
\begin{figure}[htbp]
  \center\includegraphics[height=0.7\linewidth]{figures-pdf/maxTTLCDF}
  \caption{CDF of DNS TTL value by traffic volume and by number of requests. Reprinted from \cite{PADIS2010}, \copyright ACM, 2010. Included here by permission.}
  \label{fig:CDF-IPPAF-TTL}
\end{figure}
